---
title: "Introduction to package"
author: "SA24204136 S Liu"
date: '2024-12-04'
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__SA24204136__ is a simple R package developed to use Newton-Raphson algorithm and Fisher scoring algorithm for cauchy distribution.The MLEs of most complex models are generally not explicitly expressed.At this point,numerical calculation  of MLEs is required.So we can consider Newton-Raphson algorithm and Fisher scoring algorithm.
Two functions are considered, namely, _N_ (Using Newton-Raphson algorithm for cauchy($\theta$)) and _FS_ (Using Fisher Scoring algorithm for cauchy($\theta$)). For each function, both R and Rcpp versions are produced. Namely _NR_ and  _FSR_ for R and _NC_ and _FSC_ for C++.

The source R code for _NR_ is as follows:

```{r,eval=FALSE}
NR<-function(x,theta,method){
  if(method==1){
    return(theta+sum(2*(x-theta)/(1+(x-theta)^2))/sum(2*(1-(x-theta)^2)/(1+(x-theta)^2)^2))
  }
  if(method==2){
    t<-theta+sum(2*(x-theta)/(1+(x-theta)^2))/sum(2*(1-(x-theta)^2)/(1+(x-theta)^2)^2)
    k<-1
    theta<-theta
    while(abs(theta-t)>1e-3){
      theta<-t
      t<-theta+sum(2*(x-theta)/(1+(x-theta)^2))/sum(2*(1-(x-theta)^2)/(1+(x-theta)^2)^2)
      k<-k+1
    }
    return(t)
  }
  if(method!=1 && method !=2){
    print("please input the correct method")
  }
}
```

The source Rcpp code for _NC_ is as follows:

```{r,eval=FALSE}
double NC(const NumericVector &x, double theta, int method) {
  if (method == 1) {
    return (theta + sum(2.0 * (x - theta) / (1.0 + pow(x - theta, 2))) / sum(2.0 * (1.0 - pow(x - theta, 2)) / pow(1.0 + pow(x - theta, 2), 2)));
  } else if (method == 2) {
    double t = theta + sum(2.0 * (x - theta) / (1.0 + pow(x - theta, 2))) / sum(2.0 * (1.0 - pow(x - theta, 2)) / pow(1.0 + pow(x - theta, 2), 2));
    int k = 1;
    while (std::abs(theta - t) > 1e-3) {
      theta = t;
     t = theta + sum(2.0 * (x - theta) / (1.0 + pow(x - theta, 2))) / sum(2.0 * (1.0 - pow(x - theta, 2)) / pow(1.0 + pow(x - theta, 2), 2));
     k++;
     if (k > 1000) {
       Rcpp::Rcout << "error" << std::endl;
       break;
     }
   }
   return t;
  }else{
    Rcpp::Rcout << "please input the correct method" << std::endl;
    return 0;
 }
}
```

The source R code for _FSR_ is as follows:

```{r,eval=FALSE}
FSR<-function(x,theta,method){
  if(method==1){
    return(theta+2*mean(2*(x-theta)/(1+(x-theta)^2)))
  }
  if(method==2){
    t<-theta+2*mean(2*(x-theta)/(1+(x-theta)^2))
    k<-1
    theta<-theta
    while(abs(theta-t)>1e-3){
      theta<-t
      t<-theta+2*mean(2*(x-theta)/(1+(x-theta)^2))
      k<-k+1
    }
    return(t)
  }
  if(method!=1 && method !=2){
    print("please input the correct method")
  }
}
```

The source Rcpp code for _FSC_ is as follows:

```{r,eval=FALSE}
double FSC(const NumericVector &x, double theta, int method) {
  if (method == 1) {
    return (theta + 2.0 * mean(2.0 * (x - theta) / (1.0 + pow(x - theta, 2))));
  } else if (method == 2) {
    double t = theta + 2.0 * mean(2.0 * (x - theta) / (1.0 +pow(x - theta, 2)));
    int k = 1;
    while (std::abs(theta - t) > 1e-3) {
      theta = t;
      t = theta + 2.0 * mean(2.0 * (x - theta) / (1.0 + pow(x - theta, 2)));
      k++;
      if (k > 1000) {
        Rcpp::Rcout << "error" << std::endl;
        break;
      }
    }
    return t;
  }else{
    Rcpp::Rcout << "please input the correct method" << std::endl;
    return 0;
  }
}
```


we can compare the result of one step iteration and multi-step iteration when using Newton-Raphson algorithm and Fisher scoring algorithm.

R code:

```{r}
library(SA24204136)
set.seed(1234)
n<-1000
theta<-1
n1<-n2<-f1<-f2<-numeric(n)
for(i in 1:n){
  x<-rcauchy(n,location=1)
  n1[i]<-NR(x,theta,1)
  n2[i]<-NR(x,theta,2)
  f1[i]<-FSR(x,theta,1)
  f2[i]<-FSR(x,theta,2)
}

sdn1<-sqrt(sum((n1-mean(n1))^2)/(1000-1))
sdn2<-sqrt(sum((n2-mean(n2))^2)/(1000-1))
sdf1<-sqrt(sum((f1-mean(f1))^2)/(1000-1))
sdf2<-sqrt(sum((f2-mean(f2))^2)/(1000-1))

round(c(OnestepN_theta=mean(n1),OnestepN_sd=sdn1,MultistepN_theta=mean(n2),MultistepN_sd=sdn2,OnestepF_theta=mean(f1),OnestepF_sd=sdf1,MultistepF_theta=mean(f2),MultistepF_sd=sdf2),5)
```

Rcpp code:

```{r}
n1<-n2<-f1<-f2<-numeric(n)
for(i in 1:n){
  x<-rcauchy(n,location=1)
  n1[i]<-NC(x,theta,1)
  n2[i]<-NC(x,theta,2)
  f1[i]<-FSC(x,theta,1)
  f2[i]<-FSC(x,theta,2)
}

sdn1<-sqrt(sum((n1-mean(n1))^2)/(1000-1))
sdn2<-sqrt(sum((n2-mean(n2))^2)/(1000-1))
sdf1<-sqrt(sum((f1-mean(f1))^2)/(1000-1))
sdf2<-sqrt(sum((f2-mean(f2))^2)/(1000-1))

round(c(OnestepN_theta=mean(n1),OnestepN_sd=sdn1,MultistepN_theta=mean(n2),MultistepN_sd=sdn2,OnestepF_theta=mean(f1),OnestepF_sd=sdf1,MultistepF_theta=mean(f2),MultistepF_sd=sdf2),5)
```

The results of two algorithms are basically the same.The results of one step iteration and Multi-step iteration also show that when facing cauchy distribution,they don't have too much difference.
